\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[sc]{titlesec}
\usepackage{enumerate}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{Second Conjugation}}
\fancyhead[R]{\slshape \MakeUppercase{Lesson V}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\section{\textsc{Exercises}}
\begin{enumerate}[I.]
	\setlength{\itemsep}{1em}
	\item \begin{enumerate}[1)]
		\item You have, you are teaching, you do advise.
		\item Do they scare? do they see? do they advise?
		\item We are advising, we are teaching, we have.
		\item I am warning, you have, he does scare.
		\item You are seeing, we see, he has.
		\item We frighten, I am seeing, you scare.
		\item To have, to scare, to see.
		\item You are advising, I do scare, they do teach.
		\item The stranger is teaching the poet's daughters.
		\item The pirates have the money of the inhabitants.
		\item The fortune of the daughters is delighting the woman.
		\item Who advises the inhabitants? Galba advises the inhabitants.
	\end{enumerate}
	\item \begin{enumerate}[1)]
		\item Monent, habent, moneō.
		\item Terrēs, vidēmus, docetne?
		\item Docentne puellās?
		\item Pīrātae incolās terrent.
		\item Pecūniam rēgīnae habent.
		\item Tubae sonant et columbās terrent.
	\end{enumerate}
\end{enumerate}

\section{\textsc{Conversation}}
\begin{enumerate}[1.]
	\item What do you see? We see pirates.
	\item Whom do you teach and advise? I teach and advise the stranger.
	\item Why do you love and praise the stars? Because they twinkle.
	\item Whose money does Cornelia have? Cornelia has the poet's money.
\end{enumerate}

\end{document}
