\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[sc]{titlesec}
\usepackage{enumerate}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{Predicate Nouns and Adjectives}}
\fancyhead[R]{\slshape \MakeUppercase{Lesson IX}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\section{\textsc{Review}}
\begin{enumerate}[1.]
	\item \textbf{Rule of Gender.} --- \textit{Nouns of the first declension are feminine unless they denote males}. \textbf{Rule of Gender.} --- \textit{Nouns of the second declension ending in \textbf{-um} are neuter; most others are masculine}.
	\item Nauta, agricola, Galba, poēta, advena, incola, pīrāta.
	\item The ending of the adjective is not always the same as that of the noun with which it agrees. The adjective must only agree with their nouns in gender, number, and case.
	\item It is not correct because \textbf{nauta} is a masculine noun of the first declension and \textbf{bona} is a feminine adjective of the first declension. The correct adjective would be \textbf{bonus}.
\end{enumerate}

\section{\textsc{Exercises}}
\begin{enumerate}[I.]
	\setlength{\itemsep}{1em}
	\item \begin{enumerate}[1)]
		\item Galba is strong.
		\item Galba is a farmer.
		\item My daughter is small.
		\item Is your cup large?
		\item Britain is an island of Europe.
		\item Vesta was a goddess of Rome.
		\item Galba's wagons are good and robust.
		\item The war is not pleasing.
		\item The wars are not pleasing.
		\item Stars were in the sky.
		\item Greece is a small land of Europe.
		\item I see small stars in the sky.
		\item We see small stars in the clear sky.
		\item The townsmen see Galba and the strong horses.
	\end{enumerate}
	\item \begin{enumerate}[1)]
		\item Viae oppidī sunt longae.
		\item Viae Rōmae nōn erant lātae.
		\item Viae Britanniae sunt lātae et longae.
		\item Dōna nova sunt grāta.
		\item Inimīcī pīla longa portant.
		\item Es meus amīcus cārus.
		\item Pōculum erat tuum.
	\end{enumerate}
\end{enumerate}

\end{document}
