\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[sc]{titlesec}
\usepackage{enumerate}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{Third Conjugation}}
\fancyhead[R]{\slshape \MakeUppercase{Lesson XIX}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\section{\textsc{Exercises}}
\begin{enumerate}[I.]
	\setlength{\itemsep}{1em}
	\item \begin{enumerate}[1)]
		\item He rules, he was willing, he will rule.
		\item I buy, I was buying, I shall buy.
		\item They lead, they will lead, they were leading.
		\item He has ruled, they have ruled, he has led.
		\item They have led, you have bought, you have bought.
		\item I have sent, we have sent, he has sent.
		\item We send, they send, they will send.
		\item The farmer has full fields of grain.
		\item He will send that grain into the large town.
		\item He sends this in full wagons with strong horses.
		\item Who drove those horses on the long road?
		\item He has led them, his sons, Marcus and Brutus, and today they will lead.
		\item The inhabitants of this town have bought the farmers' grain, not the wagons.
		\item The boys have brought back gold and gifts for their friends.
		\item These beautiful gifts were pleasing to their friends.
	\end{enumerate}
	\item \begin{enumerate}[1)]
		\item Regunt, regēbant, regent.
		\item Dūcit, dūcēbat, dūcet.
		\item Ēmī, ēmimus, ēmērunt.
		\item Mittō, mittam, mīsī.
		\item Mittis, mittēs, mīsistis.
		\item Mittere, emere, dūcere.
		\item Olim Rōmānī terrās multās habuērunt.
		\item Saepe nōn eōs bene regēbant.
		\item Tum incolae eārum terrārum cum audāciā pūgnāvērunt.
		\item Quod arma habuērunt?
		\item Ēius arma fuit hastae longae.
		\item Eōs mīsērunt; eīs Rōmānōs vulnerāvērunt.
	\end{enumerate}
\end{enumerate}

\end{document}
