\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[sc]{titlesec}
\usepackage{enumerate}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{First and Second Conjugations}}
\fancyhead[R]{\slshape \MakeUppercase{Lesson XIII}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\section{\textsc{Exercises}}
\begin{enumerate}[I.]
	\setlength{\itemsep}{1em}
	\item \begin{enumerate}[1)]
		\item Were they loving? he was loving, I was delighting.
		\item He was advising, they were advising, I was teaching.
		\item We were routing, they were routing, we were liberating.
		\item Were you scaring? he was having, they were having.
		\item You were seeing, you were scaring, you were adorning.
		\item We were fighting, we were calling, they were filling.
		\item The man was ploughing our field with a plough.
		\item Children were scaring the doves with trumpets.
		\item The god was surpassing the boy by means of sleep.
		\item Beautiful girls were adorning our cups with roses.
		\item Farmers were filling the wagons with grain.
		\item Mercury was the messenger of the gods.
		\item The men have arrows and spears.
	\end{enumerate}
	\item \begin{enumerate}[1)]
		\item Scūtīs.
		\item Equīs et arātrīs.
		\item Gladiīs nostrīs.
		\item Tubīs aureīs.
		\item Vidēbant, saltābatne?
		\item Librīs docēbāmus.
		\item Gladiō tuō amīcōs līberābās.
		\item Arātrō novō agrum arābam.
		\item Somnus erat grātus deō dēfessō Mercuriō.
		\item Virī hastīs et pīlīs longīs pūgnābant.
	\end{enumerate}
\end{enumerate}

\end{document}
