\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[sc]{titlesec}
\usepackage{enumerate}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{Collar and Daniell's First Year Latin}}
\fancyhead[R]{\slshape \MakeUppercase{Lesson VI}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\section{\textsc{Exercises}}
\begin{enumerate}[I.]
	\setlength{\itemsep}{1em}
	\item \begin{enumerate}[1)]
		\item The moon is showing the mistress the way.
		\item Cornelia tells the girls a story.
		\item Do the stars and the moon shine?
		\item The farmer shows the poets an island.
		\item The island is delighting the poet.
		\item And he lives on the island.
		\item The pirates remain on the water.
		\item The sailors point out the islands to the woman.
		\item The inhabitants live on the land.
		\item The pirates frighten and put to flight the women.
		\item The poets tell the daughters stories.
	\end{enumerate}
	\item \begin{enumerate}[1)]
		\item Agricolae.
		\item In īnsulīs.
		\item Incolīs.
		\item In viā.
		\item Columbīs.
		\item In viīs.
		\item In lūnā.
		\item Fīliābus.
		\item Fēminae rosam mōnstrat.
		\item Fīliābus rosās dōnant.
		\item Advenīs rosās portant.
		\item Pīrātae in īnsulā habitantne?
	\end{enumerate}
\end{enumerate}

\section{\textsc{Conversation}}
\begin{enumerate}[1.]
	\item To whom does Galba show the way? Galba shows the way to the stranger.
	\item Why do you live on the islands? Because we love the islands.
	\item To whom do you give money? I give money to the sailor.
	\item Whose doves do you set free? I set free the girl's doves.
	\item What is adorning the poet? Roses are adorning the poet.
\end{enumerate}

\end{document}
