\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[sc]{titlesec}
\usepackage{enumerate}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{Collar and Daniell's First Year Latin}}
\fancyhead[R]{\slshape \MakeUppercase{Lesson IV}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\section{\textsc{Exercises}}
\begin{enumerate}[I.]
	\setlength{\itemsep}{1em}
	\item \begin{enumerate}[1)]
		\item He delights, we put to flight, you set free.
		\item We adorn, they carry, you are delighting.
		\item We delight, you put to flight, they set free.
		\item Does he set free? I set free, we carry.
		\item To delight, to adorn, to carry.
		\item They set free the farmers' doves.
		\item The fortune of the poet delights the queen.
		\item We praise the daughters of the woman.
		\item Does the daughter of Galba adorn the queen?
		\item The stars are delighting the daughters of the sailors.
	\end{enumerate}
	\item \begin{enumerate}[1)]
		\item Terram agricolae arō.
		\item Terram agricolārum arō.
		\item Fīliae poētārum terram amant.
		\item Columbam puellae fugant.
		\item Hastāsne Galbae portant?
		\item Fīliās rēgīnārum ōrnant.
	\end{enumerate}
\end{enumerate}

\section{\textsc{Conversation}}
\begin{enumerate}[1.]
	\item Who is praising the poet? The queen's daughter is praising the poet.
	\item Do you love Galba? We love Galba.
	\item Girl, whose spear do you carry? I carry Galba's spear.
	\item Roses of whom adorn the girl? Roses of the woman adorn the girl.
	\item What do you carry? We carry arrows and a trumpet.
\end{enumerate}

\end{document}
