\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage[sc]{titlesec}
\usepackage{enumerate}

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyhead[L]{\slshape \MakeUppercase{Collar and Daniell's First Year Latin}}
\fancyhead[R]{\slshape \MakeUppercase{Lesson VII}}
\fancyfoot[C]{\thepage}
\renewcommand{\footrulewidth}{0pt}

\begin{document}

\section{\textsc{Review}}
\begin{enumerate}[1.]
	\item Nominative case. \textbf{Rule.} --- \textit{The subject of a verb is in the nominative}.
	\item Accusative case. \textbf{Rule.} --- \textit{The direct object of a transitive verb is in the accusative}.
	\item Dative case. \textbf{Rule.} --- \textit{The indirect object is in the dative}.
	\item Genitive case.
	\item \textbf{Rule.} --- \textit{A noun used to limit another, and not denoting the same person or thing, is in the genitive}.
\end{enumerate}

\section{\textsc{Exercises}}
\begin{enumerate}[I.]
	\setlength{\itemsep}{1em}
	\item \begin{enumerate}[1)]
		\item The cup is shining ; the cups are shining.
		\item I see the town ; we see the towns.
		\item Does the master advise the servant? Master, you are advising the servants.
		\item The horse loves the gift of grain.
		\item Horses of the masters are delighting the servants.
		\item Marcus tells a friend a story.
		\item Masters are giving their friends gifts of gold.
		\item We have friends in the towns.
		\item The servants are carrying grain and water for the horses.
	\end{enumerate}
	\item \begin{enumerate}[1)]
		\item Frūmentum equum dēlectat.
		\item Dōna aurī dominōs dēlectant.
		\item Habēsne amīcōs, Mārce, in hortō?
		\item Servus amīcīs vīnum in pōculīs portat.
		\item Amīcīne dōnum Mārcō mōnstrant?
		\item Oppidum et hortōs oppidī vidēmus.
		\item Domina docet.
	\end{enumerate}
\end{enumerate}

\section{\textsc{Conversation}}
\begin{enumerate}[1.]
	\item Servant, what do you have in the cup? I have wine in the cup.
	\item For whom do you carry the wine? I carry the wine in a cup for a friend.
	\item Whom is the horse frightening? The horse is frightening Cornelia.
	\item Whose horse is frightening Cornelia? Does Marcus' horse frighten Cornelia?
\end{enumerate}

\end{document}
